---
title: "hw3"
author: "Maggie Meng"
date: "2021/11/8"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(igraph)
library(data.table)
library(reshape2)
library(PearsonDS)
library(dplyr)
border_information = fread("border_information.csv", header = TRUE)
election_results = fread("election_results.csv", header = TRUE)
monthly_rainfall = fread("monthly_rainfall.csv", header = TRUE)
```


## Question 1
```{r}
#only keep integer year
monthly_rainfall$year = floor(monthly_rainfall$time)

#sum rainfall by district and year
rainfall_data <- aggregate(monthly_rainfall[, 4],
                           list(monthly_rainfall$district,monthly_rainfall$year), sum)
colnames(rainfall_data)[1] <- "district"
colnames(rainfall_data)[2] <- "year"
colnames(rainfall_data)[3] <- "rainfall"
#rainfall_data

#mean rainfall and sd rainfall
pearson <- rainfall_data %>%
  group_by(district) %>%
  mutate(mean=mean(rainfall)) %>%
  mutate(sd=sd(rainfall))

#get pnorm() of rainfall
pearson <- pearson %>% 
  mutate(p = pnorm(rainfall, mean = mean, sd = sd))

# pearson2 <- pearson %>%
#   group_by(district) %>%
#   mutate(x_mean=mean(p)) %>%
#   mutate(s=var(p))

#scale and shape
pearson2 <- pearson %>% 
  mutate(scale = sd^2/mean) %>%
  mutate(shape = (mean^2)/sd^2)

#run pearson function
pearson2$pearson <- qpearsonIII(pearson2$p, scale = pearson2$scale, shape = pearson2$shape, location = 0)

#calculate pearson mean and sd
spi <- pearson2 %>%
  group_by(district) %>%
  mutate(pearson_mean=mean(pearson)) %>%
  mutate(pearson_sd=sd(pearson))

#calculate spi
spi$spi <- (spi$pearson-spi$pearson_mean) / spi$pearson_sd

#rearrange data frame
spi_final <- spi[,c(1,2,12)]
```

```{r}
#rearrange data frame, and order by district and party name
election <- election_results[,c(2,3,7)]
election_desc = election[order(election$district,election$party_name),]

#select new found party in each district, and delete blank party name rows
election_desc2 <- election_desc %>% 
  group_by(district,party_name) %>%
  slice(which.min(year)) %>% 
  filter(party_name != "")

#count number of new founded party each year by district
party_founded <- election_desc2 %>% 
  group_by(district, year) %>% 
  mutate(n = n())
```

### A)
```{r}
q1_a <- merge(spi_final, party_founded, all = TRUE)
#q1_a2 <- q1_a[,c(1,3,4)]

#segment year to election period
q1_a_group <- q1_a %>%
  mutate(period = case_when(year <= 1951 ~ 1,
                            year > 1951 & year <= 1957 ~ 2,
                            year > 1957 & year <= 1962 ~ 3,
                            year > 1962 & year <= 1967 ~ 4,
                            year > 1967 & year <= 1971 ~ 5,
                            year > 1971 & year <= 1977 ~ 6,
                            year > 1977 & year <= 1980 ~ 7,
                            year > 1980 & year <= 1984 ~ 8,
                            year > 1984 & year <= 1985 ~ 9,
                            year > 1985 & year <= 1989 ~ 10,
                            year > 1989 & year <= 1991 ~ 11,
                            year > 1991 & year <= 1996 ~ 12,
                            year > 1996 & year <= 1998 ~ 13,
                            year > 1998 & year <= 1999 ~ 14,
                            TRUE ~ 0))

q1_a_group <- q1_a_group %>%
  mutate(num_years = case_when(period == 1 ~ 5,
                               period == 2 ~ 6,
                               period == 3 ~ 5,
                               period == 4 ~ 5,
                               period == 5 ~ 4,
                               period == 6 ~ 6,
                               period == 7 ~ 3,
                               period == 8 ~ 4,
                               period == 9 ~ 1,
                               period == 10 ~ 4,
                               period == 11 ~ 2,
                               period == 12 ~ 5,
                               period == 13 ~ 2,
                               period == 14 ~ 1,
                               TRUE ~ 0))

q1_a_group[(q1_a_group$period==1),]$num_years <- NA

#get mean spi by period in each district
q1_a_group <- q1_a_group %>%
  group_by(district,period) %>%
  mutate(spi_mean=mean(spi))
```

```{r}
#delete NA rows
q1_a_final <- q1_a_group[,-4]
q1_a_final <- q1_a_final[is.na(q1_a_group$n) == FALSE,]
q1_a_final <- q1_a_final[is.na(q1_a_final$spi) == FALSE,]
#q1_a_avg <- aggregate(x = q1_a["spi"], by = q1_a["district"], FUN = mean, na.rm = TRUE)
#q1_a_avg$n <- aggregate(x = q1_a["n"], by = q1_a["district"], FUN = sum, na.rm = TRUE)[,2]

#plot Number of Political Parties Founded vs. Average SPI
ggplot(data=q1_a_final, aes(x=n, y=spi_mean, group=1), na.omit = TRUE) +
  geom_point() +
  labs(x = "Number of Political Parties Founded", y = "Average SPI")
```

### B)
```{r}
#rearrange and rename data frame
q1_b_sqi <- q1_a_final[,c(1,5,7)]
colnames(q1_b_sqi)[1] <- "focal_district"
colnames(q1_b_sqi)[2] <- "period"
colnames(q1_b_sqi)[3] <- "neighbor_spi"

q1_b <- merge(q1_a_final, border_information, all = TRUE)

#rearrange data frame
q1_b_neighbor <- q1_b[,c(1,4,5,6,7,8)]

q1_b_neighbor <-  merge(q1_b_neighbor, q1_b_sqi, all = TRUE)

#calculate neighbor spi mean by period in each district
q1_b_neighbor_mean <- q1_b_neighbor %>%
  group_by(district,period) %>%
  mutate(neighbor_spi_mean=mean(na.omit(neighbor_spi)))

#rearrange data frame
q1_b_neighbor_mean <- q1_b_neighbor_mean[,c(3,1,4,5,6,8)]
q1_b_neighbor_mean <- unique(q1_b_neighbor_mean)

#spi lagged value
q1_b_lag <- q1_b_neighbor_mean %>%
  arrange(district,period) %>%
  group_by(district) %>%
  mutate(lag = lag(spi_mean))

#the lagged value of neighbors’ spi
q1_b_lag <- q1_b_lag %>%
  arrange(district,period) %>%
  group_by(district) %>%
  mutate(lag_neighbor = lag(neighbor_spi_mean))

#delete NA value rows
q1_b_lag <- q1_b_lag[is.na(q1_b_lag$spi_mean) == FALSE,]
```

```{r}
library(plm)
#plm(spi_mean ~ lag, q1_b_lag, effect = "twoways", model = "within", index = "district")
#plm(neighbor_spi_mean ~ lag_neighbor, q1_b_lag, effect = "twoways", model = "within", index = "district")
summary(plm(spi_mean ~ lag+lag_neighbor+num_years, q1_b_lag, effect = "twoways", model = "within", index = "district"))
```

From the result shown above, we can see that the SPI is not independent from one election period to the next within a district. They have a positive coefficient around 1, and the p value is less than 0.05, indicating that is statistically significant.

### C)
```{r}
q1_c <- q1_a_group

#assign drought and flood based on spi value
q1_c <- q1_c %>%
  arrange(district,period) %>%
  mutate(climate = case_when(spi < -1 ~ 1,
                             spi > 1 ~ 1,
                             TRUE ~ 0))

#count number of drought and flood event by period in each district
q1_c_count <- q1_c %>%
  group_by(district,period,climate) %>%
  mutate(extreme_count = sum(climate == 1 ))

#keep the max count
q1_c_count <- q1_c_count %>%
  group_by(district,period) %>%
  mutate(extreme_count = max(extreme_count))

#rearrange data frame and delete NA value rows
q1_c_count <- q1_c_count[is.na(q1_c_count$n) == FALSE,]
q1_c_count <- q1_c_count[,c(1,4,5,6,7,10)]
```

```{r}
#rearrange and rename data frame
q1_c_count2 <- unique(q1_c_count[,c(1,4,6)])
colnames(q1_c_count2)[1] <- "focal_district"
colnames(q1_c_count2)[2] <- "period"
colnames(q1_c_count2)[3] <- "neighbor_extreme_count"

#q1_c_count3 <- q1_c_count[,-2]
q1_c_neighbor <- merge(q1_c_count, border_information, all = TRUE)
q1_c_neighbor2 <- merge(q1_c_count2, q1_c_neighbor, all = TRUE)
#rearrange the order of columns
q1_c_neighbor2 <- q1_c_neighbor2[,c(4,5,6,2,7,8,1,3)]

##calculate neighbor drought and flood events mean by period in each district
q1_c_neighbor_mean2 <- q1_c_neighbor2 %>%
  arrange(district,period) %>%
  group_by(district,period) %>%
  mutate(neighbor_extreme_mean=mean(na.omit(neighbor_extreme_count)))

#rearrange data frame
q1_c_neighbor_mean2 <- q1_c_neighbor_mean2[,c(1,2,3,4,5,6,9)]
q1_c_neighbor_mean3 <- q1_c_neighbor_mean2[,-2]
q1_c_neighbor_mean3 <- unique(q1_c_neighbor_mean3)

#find lagged
q1_c_lag <- q1_c_neighbor_mean3 %>%
  #arrange(district,period) %>%
  group_by(district) %>%
  mutate(lag_extreme = shift(extreme_count))

#lagged neighbor
q1_c_lag <- q1_c_lag %>%
  arrange(district,period) %>%
  group_by(district) %>%
  mutate(lag_extreme_neighbor = shift(neighbor_extreme_mean))

#delete NA value rows
q1_c_lag <- q1_c_lag[is.na(q1_c_lag$extreme_count) == FALSE,]
```

```{r}
#see how many NAs
na_count <-sapply(q1_c_lag, function(y) sum(length(which(is.na(y)))))
data.frame(na_count)

library(pglm)

summary(pglm(extreme_count ~ lag_extreme + lag_extreme_neighbor + num_years, q1_c_lag, effect = "twoways", model = "within",  index = "district", family = "poisson"))
```

Comparing the result in part c to part b, the coefficient is close to 0, so we can conclude that the number of moderate droughts or floods is independent from one election period to the next within a district, as well as from neighboring districts from one election period to the next.


## Question 2
### A)
```{r}
q2_a = q1_c_count
summary(pglm(n ~ extreme_count + num_years, q2_a, effect = "twoways", model = "within",  index = "district", family = "poisson"))
```

```{r}
q2_b_issue = unique(election_results[,c(7,8)])
q2_b = unique(q1_c_neighbor_mean2)
q2_b = merge(q2_b_issue,q2_b)

#check all the types of party issue
unique(q2_b$party_issue)
#"liberal", "religious","economic_farming","far left","economic_nonfarming","far right","ethnic regional"
```

Liberal
```{r}
q2_b_libiral <- unique(q2_b[(q2_b$party_issue == "liberal"),c(3:8)])
summary(pglm(n ~ extreme_count + num_years, q2_b_libiral, effect = "twoways", model = "within",  index = "district", family = "poisson"))
```

Economic Farming
```{r}
q2_b_economic_farming <- unique(q2_b[(q2_b$party_issue == "economic_farming"),c(3:8)])
summary(pglm(n ~ extreme_count + num_years, q2_b_economic_farming, effect = "twoways", model = "within",  index = "district", family = "poisson"))
```

Far Left
```{r}
q2_b_far_left <- unique(q2_b[(q2_b$party_issue == "far left"),c(3:8)])
summary(pglm(n ~ extreme_count + num_years, q2_b_far_left, effect = "twoways", model = "within",  index = "district", family = "poisson"))
```

Economic Nonfarming
```{r}
q2_b_economic_nonfarming <- unique(q2_b[(q2_b$party_issue == "economic_nonfarming"),c(3:8)])
summary(pglm(n ~ extreme_count + num_years, q2_b_economic_nonfarming, effect = "twoways", model = "within",  index = "district", family = "poisson"))
```

Far Right
```{r}
q2_b_far_right <- unique(q2_b[(q2_b$party_issue == "far right"),c(3:8)])
summary(pglm(n ~ extreme_count + num_years, q2_b_far_right, effect = "twoways", model = "within",  index = "district", family = "poisson"))
```

Ethnic Regional
```{r}
q2_b_ethnic_regional <- unique(q2_b[(q2_b$party_issue == "ethnic regional"),c(3:8)])
summary(pglm(n ~ extreme_count + num_years, q2_b_ethnic_regional, effect = "twoways", model = "within",  index = "district", family = "poisson"))
```

Based on the seven regressions above, we can see that extreme weather has different effects on each political parties. By looking at the coefficients and p-value, Liberal and Far Left political parties are more likely to be formed when a district experiences extreme weather. Ethnic Regional political parties are also slightly more likely to be formed when a district experiences extreme weather. The rest of the kinds of political parties are independent from the extreme weather.

### B)
```{r}
q2_b_b <- unique(q1_c_neighbor_mean3)

#delete NA values rows
q2_b_b <- q2_b_b[is.na(q2_b_b$extreme_count) == FALSE,]

summary(pglm(n ~ extreme_count + neighbor_extreme_mean + num_years, q2_b_b, effect = "twoways", model = "within",  index = "district", family = "poisson"))
```

From the result shown above, we can see that the numbers of parties founded is independent from the number of years its neighboring districts experience years of droughts or flooding from  one election period to the next within a district. the coefficient is close to 0, and the p value is larger than 0.05, indicating that is not statistically significant.

```{r}
summary(pglm(n ~ extreme_count + neighbor_extreme_mean + num_years, q2_b_b, effect = "twoways", model = "within",  index = "district", family = "poisson"))
```


## Question 3
```{r}
#select the party name from data set
q3 <- election_results[,c(2,3,7,10)]

#segment year to election period
q3 <- q3 %>%
  mutate(period = case_when(year <= 1951 ~ 1,
                            year > 1951 & year <= 1957 ~ 2,
                            year > 1957 & year <= 1962 ~ 3,
                            year > 1962 & year <= 1967 ~ 4,
                            year > 1967 & year <= 1971 ~ 5,
                            year > 1971 & year <= 1977 ~ 6,
                            year > 1977 & year <= 1980 ~ 7,
                            year > 1980 & year <= 1984 ~ 8,
                            year > 1984 & year <= 1985 ~ 9,
                            year > 1985 & year <= 1989 ~ 10,
                            year > 1989 & year <= 1991 ~ 11,
                            year > 1991 & year <= 1996 ~ 12,
                            year > 1996 & year <= 1998 ~ 13,
                            year > 1998 & year <= 1999 ~ 14,
                            TRUE ~ 0))

q3 <- q3 %>%
  mutate(num_years = case_when(period == 1 ~ 5,
                               period == 2 ~ 6,
                               period == 3 ~ 5,
                               period == 4 ~ 5,
                               period == 5 ~ 4,
                               period == 6 ~ 6,
                               period == 7 ~ 3,
                               period == 8 ~ 4,
                               period == 9 ~ 1,
                               period == 10 ~ 4,
                               period == 11 ~ 2,
                               period == 12 ~ 5,
                               period == 13 ~ 2,
                               period == 14 ~ 1,
                               TRUE ~ 0))

q3[(q3$period==1),]$num_years <- NA
```


```{r}
#calculate the vote count of each party per election period
q3_party_vote <- q3 %>%
  arrange(district,period) %>%
  group_by(district, party_name, period) %>%
  mutate(party_vote_count = sum(vote_count))

#calculate the vote count of each district per election period
q3_party_vote <- q3_party_vote %>%
  group_by(district, period) %>%
  mutate(district_vote_count = sum(vote_count))

#calculate the vote share
q3_party_vote <- q3_party_vote %>%
  mutate(vote_share = party_vote_count/district_vote_count)

#rearrange table
q3_vote_share <- q3_party_vote[,c(1,3,5,6,9)]
q3_vote_share <- unique(q3_vote_share)
```

```{r}
#check NA values
na_count <-sapply(q3_vote_share, function(y) sum(length(which(is.na(y)))))
data.frame(na_count)

q3_vote_share <- q3_vote_share[is.na(q3_vote_share$vote_share) == FALSE,]

library(hhi)

#calculate hhi
q3_hhi <- q3_vote_share %>%
  group_by(district, period) %>%
  mutate(hhi = sum(vote_share^2))

#rearrange table
q3_hhi <- q3_hhi[,c(1,3,4,6)]
q3_hhi <- unique(q3_hhi)
```

```{r}
#get the number of extreme events
q3_count <- q1_c_count[,c(1,4,6)]

#merge two tables
q3_political <- merge(q3_count, q3_hhi, all = TRUE)

summary(pglm(hhi ~ extreme_count + num_years, q3_political, effect = "twoways", model = "within",  index = "district", family = "poisson"))
```

From the result shown above, we can see that the the HHI’s concentration (fragmentation of
political power) is independent from the extreme weather counts from one election period to the next within a district. The coefficient is close to 0, and the p value is larger than 0.05, indicating that is not statistically significant.


## Question 4
```{r}
q4 <- election_desc2 %>% 
  arrange(district,year)

q4 <- q4 %>%
  mutate(period = case_when(year <= 1951 ~ 1,
                            year > 1951 & year <= 1957 ~ 2,
                            year > 1957 & year <= 1962 ~ 3,
                            year > 1962 & year <= 1967 ~ 4,
                            year > 1967 & year <= 1971 ~ 5,
                            year > 1971 & year <= 1977 ~ 6,
                            year > 1977 & year <= 1980 ~ 7,
                            year > 1980 & year <= 1984 ~ 8,
                            year > 1984 & year <= 1985 ~ 9,
                            year > 1985 & year <= 1989 ~ 10,
                            year > 1989 & year <= 1991 ~ 11,
                            year > 1991 & year <= 1996 ~ 12,
                            year > 1996 & year <= 1998 ~ 13,
                            year > 1998 & year <= 1999 ~ 14,
                            TRUE ~ 0))

q4 <- q4 %>%
  mutate(num_years = case_when(period == 1 ~ 5,
                               period == 2 ~ 6,
                               period == 3 ~ 5,
                               period == 4 ~ 5,
                               period == 5 ~ 4,
                               period == 6 ~ 6,
                               period == 7 ~ 3,
                               period == 8 ~ 4,
                               period == 9 ~ 1,
                               period == 10 ~ 4,
                               period == 11 ~ 2,
                               period == 12 ~ 5,
                               period == 13 ~ 2,
                               period == 14 ~ 1,
                               TRUE ~ 0))

q4[(q4$period==1),]$num_years <- NA
```

```{r}
q4_neighbor <- border_information
q4_focal <- q4[,c(1,3,4)]
colnames(q4_focal)[1] <- "focal_district"
colnames(q4_focal)[2] <- "focal_party_name"
colnames(q4_focal)[3] <- "focal_period"

#neighbor district merge
q4_merge <- merge(q4, q4_neighbor, allow.cartesian=TRUE)
q4_merge <- merge(q4_merge, q4_focal, allow.cartesian=TRUE)

#rearrange table
q4_merge <- q4_merge[,c(2,5,6,4,1,8,7)]

#select neighboring district in any previous election period
q4_merge2 <- q4_merge[((q4_merge$period > q4_merge$focal_period) & 
                         (q4_merge$party_name == q4_merge$focal_party_name)),]

#rearrange table
q4_merge_final <- q4_merge2[,c(1,2,4)]

#label all parties that have contested an election in a neighboring district in any previous election period with 1
q4_merge_final <- q4_merge_final %>%
  arrange(district, period) %>%
  mutate(yes_previous = 1)

#rearrange table
q4_merge_final = unique(q4_merge_final)

q4_final <- merge(q4, q4_merge_final, all = TRUE)

#label all parties that have not contested an election in a neighboring district in any previous election period with 0
q4_final[is.na(q4_final$yes_previous),]$yes_previous <- 0
q4_final = q4_final[order(q4_final$district,q4_final$period),]
```

```{r}
#merge the number of years of droughts or flooding with previous table
q4_count <- q1_c_lag[,c(1,3,5,8)]
q4_count <- merge(q4_final, q4_count, all = TRUE)
q4_count[(is.nan(q4_count$lag_extreme_neighbor)),]$lag_extreme_neighbor <- NA
```


```{r}
q4_count_yes <- q4_count %>%
  arrange(district, period) %>%
  group_by(district, period) %>%
  mutate(n = n())

q4_count_yes <- q4_count_yes[,c(1,2,5,6,7,8,9)]
q4_count_yes <- unique(q4_count_yes)
```

```{r}
summary(pglm(yes_previous ~ extreme_count + lag_extreme_neighbor + num_years, q4_count, effect = "twoways", model = "within",  index = "district", family = "poisson"))
```

```{r}
q4_count_no <- q4_count
q4_count_no[(q4_count_no$yes_previous == 1),]$yes_previous <- NA
```


```{r}
q4_yes_previous <- q4_count[(q4_count$yes_previous == 1),]

q4_yes_previous <- q4_yes_previous %>%
  arrange(district, period) %>%
  group_by(district, period) %>%
  mutate(n = n())

q4_yes_previous <- q4_yes_previous[,c(1,2,5,7,8,9)]
q4_yes_previous <- unique(q4_yes_previous)

q4_no_previous <- q4_count[(q4_count$yes_previous == 0),]

q4_no_previous <- q4_no_previous %>%
  arrange(district, period) %>%
  group_by(district, period) %>%
  mutate(n = n())

q4_no_previous <- q4_no_previous[,c(1,2,5,7,8,9)]
q4_no_previous <- unique(q4_no_previous)
```

```{r}
summary(pglm(n ~ extreme_count + lag_extreme_neighbor + num_years, q4_yes_previous, effect = "twoways", model = "within",  index = "district", family = "poisson"))
```

```{r}
summary(pglm(n ~ extreme_count + lag_extreme_neighbor + num_years, q4_no_previous, effect = "twoways", model = "within",  index = "district", family = "poisson"))
```

Based on the two regressions above, we can see that whether the new parties that appear in a district
are the same parties that have appeared in neighboring districts in the past has different effects on number of parties founded. By looking at the coefficients and p-value, new political parties being founded in a district that have not contested an election in a neighboring district in any previous election period are more dependent to the extreme weather counts and lagged neighbor extreme weather counts. On the contrast, new political parties being founded in a district, that have contested an election in a neighboring district in any previous election period are independent to the extreme weather.










new founded parties in a district that have not contested an election in a neighboring district in any previous election period.
```{r}
library(data.table)

q4_neighbor <- border_information
q4_neighbor <- getanID(data = q4_neighbor, id.vars = "focal_district")
q4_neighbor <- dcast(setDT(q4_neighbor), focal_district ~ .id, value.var = c("district"))

q4 <- q4[,c(1,4,3)]
#q4_period <- dcast(setDT(q4), district ~ period, value.var = c("party_name"))
```

```{r}
unique_district_list <- q4_neighbor[,c(1)]

q4[(q4$district == "Adilabad"),]
test = as.list(q4_neighbor[(q4_neighbor$focal_district == "Adilabad"),])$district
#q4[(q4$district == test),]

q4[q4$district == "Adilabad" & q4$period < 3, ]$party_name

for (district_name in unique_district_list) {
  df1 = q4[(q4$district == district_name),]
  party_name = as.list(df1)$district
  neighbor = as.list(q4_neighbor[(q4_neighbor$focal_district == district_name),])$district
  
  for (i in 2:14) {
    district_party_name = as.list[(df1$period == i),]$party_name
    
    for(neighbor_name in neighbor) {
      neighbor_party = list()
      temp_neighbor_name = q4[q4$district == neighbor_name & q4$period < i, ]$party_name
      neighbor_party += temp_neighbor_name
    }
  }
  
}
```

```{r}
q4 <- q3[,c(1,3,5,6)]
q4_neighbor <- border_information

#neighbor district merge
merge(q4,border_information,allow.cartesian=TRUE)
```

new founded parties in a district, that have contested an election in a neighboring district
in any previous election period.
